\chapter{Demonstration Files}

All of the demonstration files, source code and \LaTeX{} source for this document are available for free download from my GitHub repository.

\url{https://github.com/NormanDunbar/T-Exchange/releases/latest}

\section{I Only Want the PDF Document}

\begin{enumerate}
    \item Point your browser at \url{https://github.com/NormanDunbar/T-Exchange/releases/latest}.
    \item Open up the Assets list.
    \item Right-click the PDF file and choose download.
\end{enumerate}


\section{I Want to Look at Everything}

\begin{enumerate}
    \item Go to \url{https://github.com/NormanDunbar/T-Exchange} in your browser.
    \item Click the big green ``<> Code'' button towards the top, centre right.
    \item Click ``download Zip''
    \item Uncompress the Zip file in a suitable location on your computer.
    \item Browse away to your heart's content. (See below for details of what you have in your possession!)
\end{enumerate}

\section{I'd Like to Develop this Further}

You have two options. You can simply get the code for your own use; or you can get the code with a view to making improvements and passing them back to me for inclusion in the main document etc.

\subsection{For Potential Merge Back to You!}

You will need to fork my repository as you do noty have write access to it:

\begin{enumerate}
    \item Go to \url{https://github.com/NormanDunbar/T-Exchange} in your browser.
    \item Click the small ``Fork'' button towards the top right.
    \item Click ``Create Fork''
\end{enumerate}

That's your fork created. Now, on your computer, select a suitable location and execute the following command, replacing ``YOUR-NAME'' with something appropriate:

\begin{lstlisting}
    git clone https://github.com/YOUR-NAME/T-Exchange.git
\end{lstlisting}

When you make and commit changes, and push them to your own fork, you can go to your own GitHub page for the fork, and create a merge request. Fill in the details asked for, and when done, it will get sent over to me for consideration.

\subsection{Just for Myself to Use}

You have two options, if you don't have Git installed, you can follow the instructions above to ``Look at everything''. Alternatively, if you have git installed and can use it, feel free to clone the repository to somewhere on your computer:

\begin{lstlisting}
git clone https://github.com/NormanDunbar/T-Exchange.git
\end{lstlisting}
